Learning Features and Abstract Actions for Computing Generalized Plans

### 2018-11-18 doc/arxiv-version/paper.tex
Add different arxiv version sources with hyperref package tuned

% \usepackage{soul}
% \usepackage[hidelinks]{hyperref}
% \usepackage[utf8]{inputenc}
% \usepackage[small]{caption}
%\usepackage{helvet}
%\usepackage{graphicx}
%\usepackage{url}

@@

A \emph{feature} $f$ for a class $\Q$ of problems represents a function $\phi_f$
that takes an instance $P$ from $\Q$ and a state $s$ reachable in $P$, and results
in a value denoted as $\phi_f(s)$.
A feature is \emph{boolean} if it results in boolean values, and \emph{numeric}
if it results in numerical values. %, that we assume to be a non-negative integer.
For example, $H$ and $n(x)$ represent two features in Blocksworld:
$H$ is a boolean feature that tracks whether the gripper is empty, while
$n(x)$ is numerical and tracks the number of blocks above $x$.

@@

An action $a$ and an abstract action $\bar{a}=\abst{Pre}{\Eff}$  \emph{have  the same qualitative effects over the features $F$
in a state $s$} when both are applicable in $s$ with the same effects on the boolean features and
the same \emph{qualitative effects} on the numerical features. If $s'$ is the result of applying $a$ in $s$,
this means \cite{bonet:ijcai2018}:
1)~$p \in \Eff$ and $\neg p \in Pre$ iff
$\phi_p(s)$ is false and $\phi_p(s')$ is true (i.e., $p$ becomes true),
%
2)~$\neg p \in \Eff$ and $p \in Pre$ iff
$\phi_p(s)$ is true and $\phi_p(s')$ is false ($p$ becomes false),
%
3)~$n\pplus \in \Eff$ iff $\phi_n(s') > \phi_n(s)$ ($n$ increases),
and 
%
4)~$n\mminus \in \Eff$ iff $\phi_n(s') < \phi_n(s)$ ($n$ decreases).

@@

Different assignments $\sigma$ result in different feature sets $F_{\sigma}$
and abstract action sets $A_{\sigma}$. Simpler and more meaningful features can be found
by minimizing a cost measure such as $|F_{\sigma}|$
or, more generally, $\sum_{f \in F_{\sigma}} cost(f)$.
We achieve this by casting our problem
into a constrained optimization problem, more specifically, a Weighted Max-SAT problem,
where clauses resulting from the theories $T$ or $T_G$ are taken as \emph{hard} clauses,
and we add, for each feature $f \in \F$, a
\emph{soft} unit clause $\neg selected(f)$ with weight $cost(f)$, defined below.

>>>>

% \usepackage{soul}
\usepackage[hidelinks,breaklinks=true]{hyperref}
% \usepackage[utf8]{inputenc}
% \usepackage[small]{caption}
%\usepackage{helvet}
%\usepackage{graphicx}
%\usepackage{url}

@@

A \emph{feature} $f$ for a class $\Q$ of problems represents a function $\phi_f$
that takes an instance $P$ from $\Q$ and a state $s$ reachable in $P$, and results
in a value $\phi_f(s)$.
A feature is \emph{boolean} if it results in boolean values, and \emph{numeric}
if it results in numerical values, here assumed to be non-negative.
For example, $H$ and $n(x)$ are two features in Blocksworld:
$H$, boolean, tracks whether the gripper is empty, while
$n(x)$, numerical, tracks the number of blocks above $x$.

@@

An action $a$ and an abstract action $\bar{a}=\abst{Pre}{\Eff}$  \emph{have  the same qualitative effects over the features $F$
in a state $s$} when both are applicable in $s$ with the same effects on the boolean features and
the same \emph{qualitative effects} on the numerical features. If $s'$ is the result of applying $a$ in $s$,
this means that \cite{bonet:ijcai2018}:
1)~$p \in \Eff$ and $\neg p \in Pre$ iff
$\phi_p(s)$ is false and $\phi_p(s')$ is true (i.e., $p$ becomes true),
%
2)~$\neg p \in \Eff$ and $p \in Pre$ iff
$\phi_p(s)$ is true and $\phi_p(s')$ is false ($p$ becomes false),
%
3)~$n\pplus \in \Eff$ iff $\phi_n(s') > \phi_n(s)$ ($n$ increases),
and 
%
4)~$n\mminus \in \Eff$ iff $\phi_n(s') < \phi_n(s)$ ($n$ decreases).

@@

Different assignments $\sigma$ result in different feature sets $F_{\sigma}$
and abstract action sets $A_{\sigma}$. Simpler and more meaningful features are found
by minimizing a cost measure such as $|F_{\sigma}|$
or, more generally, $\sum_{f \in F_{\sigma}} cost(f)$.
To achieve this, we cast our problem
into a constrained optimization problem, more specifically, a Weighted Max-SAT problem,
where clauses resulting from the theories $T$ or $T_G$ are taken as \emph{hard} clauses,
and we add, for each feature $f \in \F$, a
\emph{soft} unit clause $\neg selected(f)$ with weight $cost(f)$, defined below.
